Theorems and Definitions

### 2016-04-16 number_theory/hw/hw10.tex
yolo
oops
presentation

\item Suppose that $f:\NN\to\CC$ is a function such that $f(xy)=f(x)+f(y)$ for all $x,y\in\NN$. If
$f(p)=1$ for all primes $p$, prove that $f(x)=\Omega(x)$ for all $x\in\NN$.

@@

\item Let $\mu$ be the M\"{o}bius Function.
\begin{enumerate}
\item If $p$ and $q$ are distinct primes, prove that $\mu(pq)=1$.
\begin{quote}
Since $\mu$ is multiplicative, we have that $\mu(xy)=\mu(x)\mu(y)$ when $gcd(x,y)=1$. Since $p$ and
$q$ are distinct, we know that $\mu(pq)=\mu(p)\mu(q)$. By definition of the M\"{o}bius function, for
a prime $\rho$ we have
\[
\mu(\rho)=-\sum_{\substack{d\mid \rho\\d\neq\rho}}\mu(\rho)=-\mu(1)=-1,
\]
so $\mu(p)\mu(q)=(-1)(-1)=1$.
\end{quote}
\item If $p$ is prime, prove that $\mu(p^{2})=0$.
\begin{quote}
From $(a)$, we know that $\mu(\rho)=1$ for some prime $\rho$. If we consider $p^2$, we know that the
only divisors are $1,p,$ and $p^2$. By the definition of the M\"{o}bius function, we have
\[
\mu(p^2)=-\sum_{\substack{d\mid p^2\\d\neq p^2}}\mu(d)=-(\mu(1) + \mu(p))=-1 +1 = 0.
\]
\end{quote}
\item If $p$ is prime and $n$ is a positive integer, find a formula for the value of $\mu(p^{n})$.
Prove your answer.
\begin{quote}
\[
\mu(p^n)=
\begin{dcases*}
-1,\qquad n=1\\
0,\ \ \qquad n>1
\end{dcases*}
\]
Consider the value of $\mu(p^{n})$. We have already shown that $\mu(p)=-1$ for any prime $p$ and
that $\mu(p^2)=0$ for any prime. We can suppose that $\mu(p^{n})=0$ for $n\geq2$, and
$\mu(p^{n})=-1$ for $n=1$. We want to show that $\mu(p^{n+1})=0$ for $n\geq2$. Then
\begin{align*}
\mu(p^{n+1})&=-\sum_{\substack{d\mid p^{n+1}\\ d\neq p^{n+1}}}\mu(d)\\
&= -(\mu(1)+\mu(p)+\mu(p^{2})+\mu(p^{3})+\dots+\mu(p^{n}))\\
&= -(1+(-1)+0+0+\dots+0)\text{ by the inductive hypothesis}\\
&= -(0+0+0+\dots+0)\\
&= -0\\
&= 0.
\end{align*}
%If $n$ is odd, then
%we have $p^{n}=p^{2k+1}=p^{2k}p$ for some $k\in\ZZ$.
\end{quote}
\end{enumerate}

\item If $\phi$ denotes Euler's Function and $s>2$, prove that
\[
{\zeta(s-1)\over\zeta(s)}=\sum_{n=1}^{\infty}{\phi(n)\over n^{s}}.
\]
\end{enumerate}
\end{document}

>>>>

\item Suppose that $f:\NN\to\CC$ is a function such that $f(xy)=f(x)+f(y)$ for all $x,y\in\NN$. If
$f(p)=1$ for all primes $p$, prove that $f(x)=\Omega(x)$ for all $x\in\NN$.
\begin{quote}
We know that we can express $x$ and $y$ as
\begin{gather*}
x=p_{1}^{\alpha_{1}}p_{2}^{\alpha_{2}}+\dots+p_{n}^{\alpha_{n}}\\
y=p_{1}^{\beta_{1}}p_{2}^{\beta_{2}}+\dots+p_{n}^{\beta_{n}}.
\end{gather*}
We can express $f(xy)-f(y)$ as $f(x)+f(y)-f(y)=f(x)$, and we also know
\begin{align*}
f(xy)&=f(p_{1}^{\alpha_{1}+\beta_{1}}p_{2}^{\alpha_{2}+\beta_{2}}+\dots+p_{n}^{\alpha_{n}+\beta_{n}})\\
%
&= f(p_{1}^{\alpha_{1}}) + f(p_{1}^{\beta_{1}}) + f(p_{2}^{\alpha_{2}}) + f(p_{2}^{\beta_{2}})+
\dots + f(p_{n}^{\alpha_{n}}) + f(p_{n}^{\beta_{n}})\\
%
f(xy)-f(y)&=f(x)\\
&=f(p_{1}^{\alpha_{1}}p_{2}^{\alpha_{2}}\dots p_{n}^{\alpha_{n}})\\
%
&=f(p_{1}^{\alpha_{1}})+f(p_{2}^{\alpha_{2}})+\dots+f(p_{n}^{\alpha_{n}})\\
%
&=\sum_{k=1}^{\alpha_{1}}f(p_{1}) + \sum_{k=1}^{\alpha_{2}}f(p_{2}) + \dots +
\sum_{k=1}^{\alpha_{n}}f(p_{n})\\
%
&= \sum_{k=1}^{\alpha_{1}}1 + \sum_{k=1}^{\alpha_{2}}1\dots + \sum_{k=1}^{\alpha_{n}}1\\
&= \alpha_{1} + \alpha_{2} + \dots + \alpha_{n}\\
&=\Omega(x)
\end{align*}
\end{quote}

@@

\newpage
\item Let $\mu$ be the M\"{o}bius Function.
\begin{enumerate}
\item If $p$ and $q$ are distinct primes, prove that $\mu(pq)=1$.
\begin{quote}
Since $\mu$ is multiplicative, we have that $\mu(xy)=\mu(x)\mu(y)$ when $gcd(x,y)=1$. Since $p$ and
$q$ are distinct, we know that $\mu(pq)=\mu(p)\mu(q)$. By definition of the M\"{o}bius function, for
a prime $\rho$ we have
\[
\mu(\rho)=-\sum_{\substack{d\mid \rho\\d\neq\rho}}\mu(\rho)=-\mu(1)=-1,
\]
so $\mu(p)\mu(q)=(-1)(-1)=1$.
\end{quote}
\item If $p$ is prime, prove that $\mu(p^{2})=0$.
\begin{quote}
From $(a)$, we know that $\mu(\rho)=-1$ for some prime $\rho$. If we consider $p^2$, we know that the
only divisors are $1,p,$ and $p^2$. By the definition of the M\"{o}bius function, we have
\[
\mu(p^2)=-\sum_{\substack{d\mid p^2\\d\neq p^2}}\mu(d)=-(\mu(1) + \mu(p))=-1 +1 = 0.
\]
\end{quote}
\item If $p$ is prime and $n$ is a positive integer, find a formula for the value of $\mu(p^{n})$.
Prove your answer.
\begin{quote}
\[
\mu(p^n)=
\begin{dcases*}
-1,\qquad n=1\\
0,\ \ \qquad n>1
\end{dcases*}
\]
Consider the value of $\mu(p^{n})$. We have already shown that $\mu(p)=-1$ for any prime $p$ and
that $\mu(p^2)=0$ for any prime. We can suppose that $\mu(p^{n})=0$ for $n\geq2$, and
$\mu(p^{n})=-1$ for $n=1$. We want to show that $\mu(p^{n+1})=0$ for $n\geq2$. Then
\begin{align*}
\mu(p^{n+1})&=-\sum_{\substack{d\mid p^{n+1}\\ d\neq p^{n+1}}}\mu(d)\\
&= -(\mu(1)+\mu(p)+\mu(p^{2})+\mu(p^{3})+\dots+\mu(p^{n}))\\
&= -(1+(-1)+0+0+\dots+0)\text{ by the inductive hypothesis}\\
&= -(0+0+0+\dots+0)\\
&= -0\\
&= 0.
\end{align*}
\end{quote}
\end{enumerate}

% \item If $\phi$ denotes Euler's Function and $s>2$, prove that
% \[
% {\zeta(s-1)\over\zeta(s)}=\sum_{n=1}^{\infty}{\phi(n)\over n^{s}}.
% \]
\end{enumerate}
\end{document}
